### 2024-09-17 Response/Response.tex

					\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & Not consider tasks with maximum delay tolerance\\\midrule
					\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's deman into consideration \\\midrule
					\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & MADRL &  Not consider delay-sensitive tasks \\\midrule
					\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's deman into consideration\\\midrule
					\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
					\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
					\cite{wu2024combining} & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & DDPG  & Not take user's deman into consideration \\\midrule
					\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN&  Not consider tasks with maximum delay tolerance \\\midrule
					\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
					\cite{Bolourian-WCL24} & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
					QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
					\toprule
			\end{tabular}}
			\label{table1}}
	\end{table*}
	\item \underline{Reviewer's Comment}: 
	\textit{``I think more explanations should be added for the QoE function. How can the defined function reflect QoE?''} \newline

	\underline{Authors' Reply}:

	\item \underline{Reviewer's Comment}: 
	\textit{``(a) What inputs and outputs of Algorithm 2? (b) They should be added to make readers clearly understand the results.''} \\\newline
	\underline{Authors' Reply}: (a) To address the reviewer concern about algorithm 2, we have revised secound paragraph of subsection (Training Process Algorithm at EN $j \in \mathcal{J})$ in Section IV to clarify the inputs and outputs of algorithms 2, as follows. \newline

@@

\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{QECO Algorithm (Offloading Decision)}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{Input:}} \renewcommand{\algorithmicensure}{\textbf{Output:}}\Require state space $\mathcal{S}$, action space $\mathcal{A}$
			\Ensure MD $i \in \mathcal{I}$ experience  \textcolor{blue}{ $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$}
		\end{algorithmic} 
	\end{algorithm} 
\end{minipage}}
\end{my}

\vspace{10mm}
	\item \underline{Reviewer's Comment}: 
	\textit{``The authors should open their experiments in github, so that other researchers can compare their work with other ones.''} \newline
	\underline{Authors' Reply}: To address the reviewer comment, we make our experiments more accessible by sharing our GitHub rerepository. We have added it into the end of first paragraph of Section V, as follows.
	\begin{my}{1cm}{1cm}
		\rev{Detailed settings regarding the neural networks and simulation can be found at our github repository. }
	\end{my}
	We have also provided repository URL link in the footnote of Page 8 as below.
	\begin{my}{1cm}{1cm}
		\rev{The code for reproducing the simulation results of this letter is available at\newline https://github.com/ImanRHT/QECO.} \newline
	\end{my}

	\item \underline{Reviewer's Comment}: 
	\textit{``The following references closely related to the current work should be discussed or compared with the current work for completeness.''} \newline
		\begin{my}{1cm}{1cm}
		\rev{
			{\small
				\noindent\hspace{-0.5mm}\cite{wu2024combining}  G. Wu, X. Chen, Y. Shen, Z. Xu, H. Zhang, S. Shen, and S. Yu,``Combining Lyapunov optimization with Actor-Critic networks for privacy-aware IIoT computation offloading,'' in \textit{IEEE Internet of Things Journal}, 2024, Early Access\\[6pt]
				\cite{wu2023computation} G. Wu, H. Wang, H. Zhang, Y. Zhao, S. Yu, and S. Shen, ``Computation offloading method using stochastic games for software-defined-network-based multiagent mobile edge computing,'' \textit{IEEE Internet of Things Journal}, vol. 10, no. 20, pp. 17620–17634, Oct. 2023.\\[6pt]
				\cite{wu2024privacy} G. Wu, X. Chen, Z. Gao, H. Zhang, S. Yu, and S. Shen, ``Privacy-preserving offloading scheme in multi-access mobile edge computing based on MADRL,'' \textit{Journal of Parallel and Distributed Computing}, vol. 10, no. 1, pp. 451--460, Mar. 2022.\\[6pt]
				\cite{wu2023multi} G. Wu, Z. Xu, H. Zhang, S. Shen, and S. Yu,  ``Multi-agent DRL for joint completion delay and energy consumption with queuing theory in MEC-based IIoT,'' in \textit{Journal of Parallel and Distributed Computing}, vol. 176, pp. 80–94, Jun. 2023\\[10pt]}\\}
	\end{my}
